---
title: "Market Value of Fortune 500 Companies"
execute: 
  echo: false
date: "`r Sys.Date()`"
sidebar: false
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(readr)
library(rstanarm)
library(gtsummary)
```

```{r}
train <- read_csv('data/Cleaned Data.csv', show_col_types = FALSE) |>
  select(market_value_mil, year, revenue_mil, profit_mil, asset_mil, employees) |>
  drop_na()
```

```{r}
fit_obj <- stan_glm(formula = market_value_mil ~ year + revenue_mil + profit_mil + asset_mil + employees,
                    data = train,
                    refresh = 0,
                    seed = 42)
```

```{r}
newobs = tibble(year = 2023, 
                revenue_mil = 35000,
                profit_mil = 3500,
                asset_mil = 110000,
                employees = c(100000,250000,500000,750000,1000000))

pe <- posterior_epred(fit_obj, newdata = newobs) |> 
  as_tibble()
```

```{r}
colnames(pe)[colnames(pe) == 1] = '100000'
colnames(pe)[colnames(pe) == 2] = '250000'
colnames(pe)[colnames(pe) == 3] = '500000'
colnames(pe)[colnames(pe) == 4] = '750000'
colnames(pe)[colnames(pe) == 5] = '1000000'
```

```{r}
pe <- pe |> 
  pivot_longer(cols = c('100000','250000','500000','750000','1000000'), 
               names_to = "number_of_employees",
               values_to = "market_value")
pe$number_of_employees <- as.numeric(pe$number_of_employees)
pe$number_of_employees <- as.factor(pe$number_of_employees)
```

```{r}
#| message: false
#| warning: false
pe |>
  ggplot(aes(market_value, fill = number_of_employees)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                   alpha = 0.5, 
                   bins = 100, 
                   position = "identity") +
  labs(title = "Posterior for Market Value",
       subtitle = "Fortune 500 Companies with more employees have higher market value.",
       x = "Market Value ($m)",
       y = "Probability",
       caption = 'fortune.com',
       fill = "Number of Employees") + 
  scale_x_continuous(labels = scales::comma_format()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_fill_discrete(labels = c('100,000','250,000','500,000','750,000','1,000,000')) +
  theme_classic()
```

Fortune 500 companies have been the bedrock of the global economy and represent two-thirds of the United States' GDP. The data was scraped from Fortune and uploaded to Kaggle. Then, the data was cleaned and visualized. Finally, I estimated a Bayesian regression model with market value as the dependent variable and year, revenue, profit, and assets as the independent variables.